Planning for Quasi-Periodic and Secular Variability of Climate Risk

### 2018-04-04 writeup/main.tex
Continue writing

The \nth{20} century saw the evolution of a nearly universal approach to the statistical analysis of weather and climate hazard.
In this framework, event risk is assessed as a relationship between the event magnitude and its annual probability of exceedance.
Under the assumption that the historical or simulated record of events constitutes an stationary, \gls{iid} process, and using an appropriate statistical inference model, an estimate of this relationship and its uncertainty based on a finite $N$-year record is developed.
This is then used as a measure for decision analysis for infrastructure, flood zoning and insurance instruments for event risk mitigation applied to the costs and residual losses expected from the mitigation instrument.
The uncertainty associated with the model may be used to develop a risk premium for insurance, or for assessing the potential over- or under- design of infrastructure.

Over time it has become clear that even small fluctuations in the dynamics of the hydroclimate system, known as nonstationarities \citep{Milly2008}, can lead to clustering of extreme events  and strong time dependence of a public or private actor's risk profile \citep{Bonnafous2017a,Bonnafous2017b}.
For example, in 2011 four typhoons struck northern Thailand \citep{Gale2013}, causing severe damage to public and private infrastructure and crippling global supply chains \citep{Haraguchi2015}.
Similarly, in June 2013 three summertime cyclones followed highly similar tracks, leading to widespread flooding in central Europe \citep{Grams2014}.
More recently the 2017 Atlantic hurricane season led to over \usd{130 billion} in insured losses \citep{SwissRe2017}, despite negligible losses in the preceding several years.
Each of these events was highly improbable under \gls{iid} assumptions, yet the clustering of such events is well-documented in the literature \citep{Hurst1951,Matalas2012,Merz2014} and is consistent with our understanding of the nonlinear dynamics of the climate system \citep{Hannachi2017}.

Nonstationarity behavior that leads to violation of traditional assumptions takes two primary forms.
The first, secular change, may be related to anthropogenic climate change, river modification, or land use change \citep{Merz2014}.
The uncertainties associated with this are not purely informational, at least in the sense that they can be inferred from a historical sample or model.
Both nature and human actions over the course of this century will determine the magnitude and direction of secular change, and neither is fully predictable.
The uncertainty associated with secular change clearly grows as one looks out into the distant future, and the importance of investment decisions that may engage us in considerations of designs that go far out into the future, \eg{} 2100, diminish if any positive discount rate is used for the future.
While this consideration offsets the impact of the growing uncertainty for longer project life, it also suggests that it may be more effective to understand the consequences for analysis that may focus on shorter lived adaptation strategies which may last for 1, 5, 10, 20,  30 or 50 years.

@@

@@

\subsection{Are Generated Sequences Realistic?\label{sec:sequence-realistic}}

>>>>

Hydroclimate systems exhibit organized low-frequency and regime-like structure which cause the reliability of physical structures and financial instruments used for risk management to vary across timescales \citep{Jain2001,Merz2014,Hannachi2017}.
This phenomenon, termed nonstationarity \citep{Milly2008} violates the core assumptions made in classical statistical analysis of weather and climate hazard, in which an $N$-year historical record is assumed to represent \gls{iid} draws from a stationary distribution in order to estimate a relationship between event magnitude and its probability of occurrence.
This is then used as a measure for decision analysis for infrastructure, flood zoning and insurance instruments for event risk mitigation applied to the costs and residual losses expected from the mitigation instrument.
The uncertainty associated with the model may be used to develop a risk premium for insurance, or for assessing the potential over- or under- design of infrastructure.

The nonstationarity behavior which violates these assumptions takes two primary forms.
The first, secular change, may be related to anthropogenic climate change, river modification, or land use change \citep{Merz2014}.
The uncertainties associated with this are not purely informational, at least in the sense that they can be inferred from a historical sample or model.
Both nature and human actions over the course of this century will determine the magnitude and direction of secular change, and neither is fully predictable.
The uncertainty associated with secular change clearly grows as one looks out into the distant future, and the importance of investment decisions that may engage us in considerations of designs that go far out into the future, \eg{} 2100, diminish if any positive discount rate is used for the future.
While this consideration offsets the impact of the growing uncertainty for longer project life, it also suggests that it may be more effective to understand the consequences for analysis that may focus on shorter lived adaptation strategies which may last for 1, 5, 10, 20,  30 or 50 years.

@@

Given that these risk mitigation instruments are typically evaluated over a $M$-year period and based on an $N$-year historical record, the potential of a regime shift can lead to a dramatic over- or under-design of the designed instrument.
If a physical regime associated with hydroclimate variability has duration $D$ which is of order $N$, then it is unlikely that 
Now signal that it is important to then understand how the linkage of regimes of duration D influences risk, and what implications it has for detection given N and mis-classification given M

% Perceptions about 100 year flood?
For example, in 2011 four typhoons struck northern Thailand \citep{Gale2013}, causing severe damage to public and private infrastructure and crippling global supply chains \citep{Haraguchi2015}.
Similarly, in June 2013 three summertime cyclones followed highly similar tracks, leading to widespread flooding in central Europe \citep{Grams2014}.
More recently the 2017 Atlantic hurricane season led to over \usd{130 billion} in insured losses \citep{SwissRe2017}, despite negligible losses in the preceding several years.
Each of these events was highly improbable under \gls{iid} assumptions, yet the clustering of such events is well-documented in the literature \citep{Hurst1951,Matalas2012,Merz2014} and is consistent with our understanding of the nonlinear dynamics of the climate system \citep{Hannachi2017}.
This behavior is generically known as nonstationarity \citep{Milly2008}, and has been shown to lead to clustering of extreme events and strong time dependence of a public or private actor's risk profile \citep{Bonnafous2017a,Bonnafous2017b}.

@@

\section{Supplemental Results}

\subsubsection{Are Generated Sequences Realistic?\label{sec:sequence-realistic}}
